\chapter{Conclusions}
\label{chapter:conclusions}

Data obtained in \textit{Data Analysis} section \ref{sec:analysis} reveals that underground forums as HackForums are clearly lossing market activity over last years. Sale of access IoT devices services for DDoS has been a very important topic in the market section, but the current trend is downward and it is no longer a topic of great relevance. 

However, the data obtained in this study do not allow us to affirm that the sale of this type of services has lost importance. Other forms of communication such as Telegram or Discord channels or other social networks could be gaining users to the detriment of this type of web forums. It could be due to its higher level of anonymity, ease of use and instant messaging benefits.

Regarding supply and demand, it seems that the interest of potential buyers has been declining and there is more activity in the supply than interest in buying. Although as an exception, it seems that services with a stress-as-a-service approach currently continue to have more demand than supply. Which suggests that there is a niche of professional buyers interested in hiring criminal services in order to test the resilience of their network systems.

Preferred payment methods have evolved significantly. The use of cryptocurrencies, more specifically Bitcoin, as a preferred payment method has been growing, being clearly more used nowadays. As we discussed earlier regarding forms of communication, the adoption of cryptocurrencies could be due to their higher level of anonymity, ease of use, and availability around the world. 